A Survey of Physical Design Techniques of Information Systems

### 2010-07-10 cs848-db/Paper.tex

\subsection{Data Compression}

\subsection{Other Techniques}

Striping, mirroring, denormalization.

@@

Given the different physical design methods explained in the previous section, we now look at how these methods apply to different types of information systems.
Mainly, how they apply to Disk-based relational database systems, main memory relational database systems, data warehouses, and XML databases.

@@

\subsubsection{Type of Indexes Used}

@@

\subsubsection{Indexes}
\paragraph{Tree-based Indexes}
B-tree (B+ trees but commonly referred to as B-trees) \cite{253268}, R-tree \cite{602266, Cheung20011}, K-D-B-tree \cite{582321}, BV-tree \cite{223796}, UB-tree
\cite{bayer1997universal}

>>>>

\subsection{Other Physical Design Techniques}

There are other physical design methods to improve the performance of the information systems~\cite{lightstone2007physical}. For example, data compression can
be used to make more data fit into a fixed amount of disk space such that it can be access faster. Data striping is used to distribute data that is accessed
together across multiple disks. This allows the data to be retrieved faster through parallelism. Database reliability is also improved through mirorring which
involves duplicating the data on multiple disks. Finally, refining the global schema to reflect query and transaction requirements is also sometimes used. This
is called denormalization.

@@

Given the different physical design methods explained in the previous section, we now look at how these methods apply to different types of information systems.
Mainly, how they apply to Disk-based relational database systems, main memory relational database systems, data warehouses, and XML databases. We mainly focus
on the first four techniques discussed in Section~\ref{SEC-ELEMENTS} as these are the main design decisions involved in physical design.

@@

@@

\subsubsection{Index Structures}
\paragraph{Tree-based Indexes}
B-tree (B+ trees but commonly referred to as B-trees) \cite{253268}, R-tree \cite{602266, Cheung20011}, K-D-B-tree \cite{582321}, BV-tree \cite{223796}, UB-tree
\cite{bayer1997universal}
